---
title: "Homework One"
author: "Rachel Meredith"
date: "1/26/2022"
output:
  pdf_document: default
  html_document: default
---
```{r}
library(tidyverse)
library(kableExtra)
library(datasets)
tinytex::install_tinytex()
```
## R Markdown

# Q14

a.)
My Data set
```{r}
data_set <- read.csv("C:/Users/rache/Documents/STAT 3010/Hw1_Q14_data.csv", header = T)
```
Stem Plot
```{r}
stem(data_set$shower_flow_rate)
```

capture.output(stem(data_set$score))
file <- "C:/Users/rache/Documents/STAT 3010/Ex.1.2_Q14_data.txt"

b.)
Typical flow rate is the flow rate that appears the most. So we would take one of the values from 6. ex = 6.7

c.)
Highly concentrated, only one outlier. 

d.)
distribution is left skewed since there are more values below the typical flow rate.

e.)
Outlier would be 18.9.

# 22.)

a.) sample size = 90 + 190 + 180 + 160 + 120 + 80 + 60 + 40 + 30 + 20 = 970

runners = 10

p = (# of runners) / (sample size)

p = 10 / 970 = 0.01

# 24.) 
My data set
```{r}
setwd("C:/Users/rache/Documents/STAT 3010")
data_set2 <- read.csv("Hw1_Q24_data.csv")

head(data_set2)
we = data_set2[,1]
```

My Histogram
```{r}
hist(we)
```

# 34.)
```{r}
setwd("C:/Users/rache/Documents/STAT 3010")
data_set3 <- read.csv("Hw1_Q34_data.csv")
```
a.) Sample mean
homes = (6 + 5 + 11 + 33 + 4 + 5 + 80 + 18 + 35 + 17 + 23)/11= 21.55EU/mg

b.)
farm homes = (2+15+12+8+8+7+6+19+3+9.8+22+9.6+2+2+0.5)/15 = 8.39

c.)
ascending order
4,5,5,6,11,17,18,23,33,35,80
n = 11
((11+1)/2)th position = median is 17 EU/mg for urban homes.

ascending order
0.5,2,2,2,3,6,7,8,8,9.6,12,15,19,22
n=15
((15+1)/2)th position = median is 8 EU/mg for farm houses.

c.)
trimmed mean = (6+5+11+33+5+18+35+17+23)/9= 17.00 for urban houses

trimmed mean = (2+15+12+8+8+7+6+19+3+9.8+9.6+2+2)/13 = 7.95 for farm houses.

(1 * 100)/11= 9.09% <-urban home trimming percentage
(1 * 100)/15 = 6.67% <- farmhouse trimming percentage

# 35.)
```{r}
data_set4 <- read.csv("C:/Users/rache/Documents/STAT 3010/Hw1_Q35_data.csv.xls")

# a.)

x <- c(data_set4)
result.mean <- mean(data_set4,trim = 0)
print(result.mean)

```

# 53
a.)
n is odd so median is 2.74

Upper fourth meadian is 3.88

3.88 - 2.74 = 1.14

b.) 
my data set
```{r}
data_set53 <- read.csv("C:/Users/rache/Documents/STAT 3010/Hw1_Q53_data.csv")
```
boxplot
```{r}
boxplot(data_set53, xlab= "Percentage of Assets", ylab = "Growth and Blended Funds", ylim= c(0,4))
```

#56
data set:
```{r}
data_set56 <- read.csv("C:/Users/rache/Documents/STAT 3010/Hw1_Q56_data.csv")
```
boxplot
```{r}
boxplot(data_set56, xlab= "", ylab = "", ylim= c(0,25))
```

# 58
a.)

Machine 1 has a small data variation but machine 2 has a high data variation. Machine 1 also has an outlier but machine 2 does not. 

